Sex-specific Meta-analysis in MSSM-Penn-Pitt and HBCC ACC/DLPFC

### 2020-07-29 individual-cohorts/graphics_t_statistics.Rmd

```{r setup, include=FALSE}
library(synapser)
synLogin()
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(ComplexHeatmap)
library(readxl)
library(gtools)
library(corrplot)
library(pvclust)

@@

```{r synapse.parameters, include=FALSE, cache=TRUE, eval=FALSE}
thisFileName <- 'graphics_t_statistics.Rmd'

>>>>

```{r setup, include=FALSE}
library(synapser)
synLogin()
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(ComplexHeatmap)
library(readxl)
library(gtools)
library(corrplot)
library(pvclust)
library(metafor)

@@

```{r synapse.parameters, include=FALSE, cache=FALSE, eval=FALSE}
thisFileName <- 'graphics_t_statistics.Rmd'
